---
title: "Calibration and Simple Optimization"
author: "Paige FitzGibbon"
date: "May 31, 2019"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE}

library(tidyverse)
library(dplyr)
library(sensitivity)

#Functions from Lecture
source("compute profit.R")
source("compute yield.R")
source("compute NPV.R")

```



Create a graph of optimal irrigation purchase as the most of irrigation goes from $1 to $100

```{r}
crop_pars = c(ts = 0.4, tp = 0.5, base.yield = 500, Topt = 25, max.water = 800)
cost <-  seq(1,100,by=1)

opt_results_maximum <- NA
opt_results_objective <-NA

df1 <- data.frame(cost=cost, opt_results_maximum=opt_results_maximum, opt_results_objective=opt_results_objective)

for (i in 1:nrow(df1)) {
  
  results_raw = optimize(compute_profit, lower =0, upper=100000, T=c(20,30,25), P=c(250,144,100), discount=0.01,price=50,cost=df1$cost[i], crop.pars=crop_pars, maximum=TRUE)

  df1$opt_results_maximum[i] = results_raw[[1]]
  df1$opt_results_objective[i] = results_raw[[2]]
  
}

ggplot(df1, aes(x=cost, opt_results_maximum))+
  geom_line(color="blue")+
  theme_classic()+
  labs(title = "Optimal Irrgation Purchase")+
  ylab("Water Purchased (mm)")+
  xlab("Cost ($)")

```


Perform a sobel sensitivity analysis to vary the temperature and precipitation of the 3 years, the price for the crop and then cost of water - calculate the optimal irrigation for each parameter set

```{r}
Temp1 = cbind.data.frame(
  T1 = runif(min=-10, max=40, n=50),
  T2 = runif(min=-10, max=40, n=50))

Temp2 = cbind.data.frame(
  T1 = runif(min=-10, max=40, n=50),
  T2 = runif(min=-10, max=40, n=50))
Precip1 = cbind.data.frame(
  P1 = runif(min=0, max=1000, n=50),
  P2 = runif(min=0, max=1000, n=50))
Precip2 = cbind.data.frame(
  P1 = runif(min=0, max=1000, n=50),
  P2 = runif(min=0, max=1000, n=50))
Cost1 = cbind.data.frame(
  c1 = runif(min=1, max=100, n=50))
Cost2 = cbind.data.frame(
  c1 = runif(min=1, max=100, n=50))
Price1 = cbind.data.frame(Pr1 = runif(min=0, max=100, n=50))
Price2 = cbind.data.frame(Pr1 = runif(min=0, max=100, n=50))
Allparams_sens1 = cbind.data.frame(Temp1, Precip1, Cost1, Price1)
Allparams_sens2 = cbind.data.frame(Temp2, Precip2, Cost2, Price2)
sens_optimize = sobol2007(model = NULL, Allparams_sens1, Allparams_sens2, nboot = 100)
nsim=nrow(sens_optimize$X)
irrigation_results = rep(0,times=nsim)
cost <- as.numeric(sens_optimize$X$c1)
opt_results_maximum <- NA
opt_results_objective <-NA

results <- data.frame(cost=cost,
                      opt_results_maximum=opt_results_maximum, 
                      opt_results_objective=opt_results_objective)

for (i in 1:nsim) {
  
tmp = optimize(compute_profit, lower = 0, upper=100000,
                       T=as.numeric(sens_optimize$X[i,c("T1","T2")]),
                       P=as.numeric(sens_optimize$X[i,c("P1","P2")]),
                       discount=0.01,
                       price=as.numeric(sens_optimize$X[i,"Pr1"]),
                       cost=results$cost[i], 
                       crop.pars=crop_pars,
                       maximum=TRUE)

  results$opt_results_maximum[i] = tmp[[1]]
  results$opt_results_objective[i] = tmp[[2]]
  irrigation_results[i] = results$opt_results_maximum[i]

    }

sensitivity = sensitivity::tell(sens_optimize, irrigation_results)

plot(sensitivity)

```

Price and cost have more impact on irrigation optimization than temperature and precipitation. The optimal irrigation varies based on the randomly generated parameters.  
